Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-11-29 paper/main.tex

\newcommand{\lsst}{\textsc{LSST}}
\newcommand{\lsstdesc}{\lsst\textsc{-DESC}}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{\pz\ PDF}% can easily change this to specify posterior throughout

@@

The authors would like to thank their LSST-DESC publication review committee.

@@

>>>>

\newcommand{\lsst}{\textsc{LSST}}
\newcommand{\lsstdesc}{\lsst\textsc{-DESC}}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{\pz\ PDF}% can easily change this to specify posterior throughout
\newcommand{\qp}{\texttt{qp}}

@@

The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.

{ \red{personal funding sources}}

@@

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn}, \textsc{minFunc} \citep{minfunc}, \textsc{pySkyNet} \citep{pyskynet}, and {\textsc photUtils} from the LSST simulations package \citep{lsstphotutils}.
